---
title: "Program"
subtitle: "Last Modified: 2023-02-09"
---

```{r} 
parallels <- 5
sessions <- 3
talks <- 6
total <- parallels * sessions * talks
```

## [At a glance]{.highlight}

### Themes

8 general sessions and 8 special symposia:

```{r} 
library(kableExtra)
library(tidyverse)

themes <- tribble(
  ~"General sessions", ~"Special symposia",
"Bio-mediated methods for hazard mitigation                        ", "Bio-inspired Tunneling                         ",
"Bio-mediated methods for environmental protection and restoration ", "Asia experiences on bio-mediated geotechnics   ",
"Bio-mediated methods for infrastructure construction              ", "Europe experiences on bio-mediated geotechnics ",
"Bio-inspired methods for infrastructure construction              ", "Biopolymer treated soils                       ",
"Bio-inspired methods for subsurface exploration and excavation    ", "Delivery strategies for MICP                   ",
"Fundamental research on biogeotechnics                            ", "MICP for sustainable geoenergy applications    ",
"Case studies on field applications of biogeotechnics              ", "Fungal treatment of soils                      ",
"Education and outreach in biogeotechnics                          ", "Build with nature                              ",
) 
kbl(themes) %>%
  column_spec(1, background = "#c4996c") %>%
  row_spec(0, background = "#747474")
```

* 4 plenary sessions: 
  * 3 general reports
  * 6 keynote lectures
  * 1 panel discussion
* `r parallels` general sessions:
  * `r sessions` parallel sessions
  * `r talks` presentations in each session
  * `r total` presentations in total
* 1 poster session


##  Monday, May 19, 2025

: {.hover}

| Time  | Event                                                                     |
| ----- | ------------------------------------------------------------------------- |
| 8:00  | Registration                                                              |
| 8:30  | Plenary Session 1                                                         |
|       | 10 min: Welcome: Conference Chairs                                        |
|       | 30 min: General report on Bio-mediated  Geotechnics                       |
|       | 30 min: General report on Bio-inspired Geotechnics                        |
|       | 20 min: General report on Education and Outreach                          |
| 10:00 | coffee break                                                              |
| 10:30 | Plenary Session 2                                                         |
|       | 30 min: Keynote 1: Bio-mediated Geotechnics/Hazard Mitigation             |
|       | 30 min: Keynote 2: Bio-inspired Geotechnics/Infrastructure                |
|       | 30 min: Keynote 3: Industry Perspectives on Biogeotechnics                |
| 12:00 | lunchbreak                                                                |
| 13:00 | General Session 1                                                         |
|       | GS 1a: 6 x 15 min presentations                                           |
|       | GS 1b: 6 x 15 min presentations                                           |
|       | GS 1c: 6 x 15 min presentations                                           |
| 14:30 | coffee break                                                              |
| 15:00 | General Session 2                                                         |
|       | GS 2a: 6 x 15 min presentations                                           |
|       | GS 2b: 6 x 15 min presentations                                           |
|       | GS 2c: 6 x 15 min presentations                                           |
| 16:30 | End of sessions                                                           |
| 16:45 | Poster Session w/ hors d’oeuvres and cash bar (1 drink ticket per person) |
| 18:30 | End of day 1                                                              |

\newpage

##  Tuesday, May 20, 2025

: {.hover}

| Time  | Event                                                                     |
| ----- | ------------------------------------------------------------------------- |
| 8:00  | Registration                                                              |
| 8:30  | Plenary Session 3                                                         |
|       | Keynote 4: Bio-mediated Geotechnics/Environmental                         |
|       | Keynote 5: Bio-inspired Geotechnics/Probes and Tunneling                  |
|       | Keynote 6: Bio-mediated Geotechnics/Infrastructure                        |
| 10:00 | coffee break                                                              |
| 10:30 | General Session 3                                                         |
|       | GS 3a: 6 x 15 min presentations                                           |
|       | GS 3b: 6 x 15 min presentations                                           |
|       | GS 3c: 6 x 15 min presentations                                           |
| 12:00 | lunchbreak                                                                |
| 13:00 | General Session 4                                                         |
|       | GS 4a: 6 x 15 min presentations                                           |
|       | GS 4b: 6 x 15 min presentations                                           |
|       | GS 4c: 6 x 15 min presentations                                           |
| 14:30 | coffee break                                                              |
| 15:00 | General Session 5                                                         |
|       | GS 5a: 6 x 15 min presentations                                           |
|       | GS 5b: 6 x 15 min presentations                                           |
|       | GS 5c: 6 x 15 min presentations                                           |
| 16:30 | End of sessions                                                           |
| 16:45 | Plenary Session 4: Panel discussion: Future directions for biogeotechnics |
| 17:45 | Closing Remarks: Conference Chairs                                        |
| 18:00 | Banquet and award ceremony                                                |


::: {.content-visible when-profile="local"}

::: {.callout-note}

* Based on this original plan, there will be 12 plenary talks, 72 presentations in parallel sessions, and a number of poster presentations in 2 poster sessions.

* We may want to reduce the number of plenary talks to make room for more parallel sessions. 

* We can have at least three tracks:
  * Bio-mediated Geotechnics
  * Bio-inspired Geotechnics
  * Education, training, industrial collaboration, sustainability in Biogeotechnics

* For each track, we can have a few sessions targeting on different applications such as:
  * Bio-mediated
    * Hazard mitigation
    * Construction
    * Environmental remediation or restoration
  * Bio-inspired
    * Site investigation
    * Foundation
    * Cross-cutting
  * ETCS (successes and pitfalls)
    * Education
    * Training
    * Industrial collaborations
    * Sustainability

:::
:::

