---
title: "Program"
subtitle: "Last Modified: 2024-12-16"
---

```{r} 
parallels <- 6+4/6 
sessions <- 3
talks <- 6
total <- parallels * sessions * talks
```

## At a glance

* 8 general themes
* 8 special symposia
* 7 plenary sessions: 
  * 6 keynote lectures
  * 1 poster session
* `r round(parallels)` oral presentation sessions:
  * `r sessions` parallel sessions
  * `r talks` presentations in each parallel session
  * `r total` presentations in total

```{r} 
library(kableExtra)
library(tidyverse)

themes <- tribble(
  ~"General sessions", ~"Special symposia",
"Bio-mediated methods for hazard mitigation                        ", "Bio-inspired Tunneling                         ",
"Bio-mediated methods for environmental protection and restoration ", "Asia experiences on bio-mediated geotechnics   ",
"Bio-mediated methods for infrastructure construction              ", "Europe experiences on bio-mediated geotechnics ",
"Bio-inspired methods for infrastructure construction              ", "Biopolymer treated soils                       ",
"Bio-inspired methods for subsurface exploration and excavation    ", "Delivery strategies for MICP                   ",
"Fundamental research on biogeotechnics                            ", "MICP for sustainable geoenergy applications    ",
"Case studies on field applications of biogeotechnics              ", "Fungal treatment of soils                      ",
"Education, outreach, diversity, inclusion and equity in engineering", "Build with nature                              ",
) 
kbl(themes) %>%
  column_spec(1, background = "#c4996c") %>%
  row_spec(0, background = "#747474")
```


## Sunday, May 18, 2025

| Time        | Event                                                                                               |
|-------------|-----------------------------------------------------------------------------------------------------|
| 4:00-7:00pm | Welcome Reception at [**Paul C. Helmick Center (HLMK)**](https://maps.app.goo.gl/UAZTpkQkEPtLqvf86) |

## Monday, May 19, 2025

Meetings at [**Memorial Union**](https://eoss.asu.edu/mu)

: {.hover}

| Time          | Event          | Track 1   | Track 2   | Track 3   |
|---------------|----------------|-----------|-----------|-----------|
| 7:45-8:00am   | Opening Remark |           |           |           |
| 8:00-8:40am   | Keynote 1      |           |           |           |
| 8:40-8:50am   | 10 min Break   |           |           |           |
| 8:50-10:20am  |                | Session 1 | Session 2 | Session 3 |
| 10:20-10:40am | 20 min Break   |           |           |           |
| 10:40-12:10pm |                | Session 4 | Session 5 | Session 6 |
| 12:10-1:10pm  | Lunch Break    |           |           |           |
| 1:10-1:50pm   | Keynote 2      |           |           |           |
| 1:50-2:50pm   | Poster Session |           |           |           |
| 2:50-4:20pm   |                | Session 7 | Session 8 | Session 9 |
| 4:20-4:50pm   | 30 min Break   |           |           |           |
| 4:50-5:30pm   | Keynote 3      |           |           |           |

\newpage

##  Tuesday, May 20, 2025

: {.hover}

| Time          | Event                                                              | Track 1    | Track 2    | Track 3    |
|---------------|--------------------------------------------------------------------|------------|------------|------------|
| 8:00-8:40am   | Keynote 4                                                          |            |            |            |
| 8:40-8:50am   | 10 min Break                                                       |            |            |            |
| 8:50-10:20am  |                                                                    | Session 10 | Session 11 | Session 12 |
| 10:20-10:40am | 20 min Break                                                       |            |            |            |
| 10:40-12:10am |                                                                    | Session 13 | Session 14 | Session 15 |
| 12:10-1:10am  | Lunch Break                                                        |            |            |            |
| 1:10-1:50pm   | Keynote 5                                                          |            |            |            |
| 1:50-2:00pm   | 10 min Break                                                       |            |            |            |
| 1:50-3:20pm   |                                                                    | Session 16 | Session 17 | Session 18 |
| 3:20-3:50pm   | 30 min Break                                                       |            |            |            |
| 3:50-4:50pm   |                                                                    | Session 19 | Session 20 | Session 21 |
| 4:50-5:30pm   | Keynote 6                                                          |            |            |            |
| 5:30-5:45pm   | Closing Remarks                                                    |            |            |            |
| 6:00-9:00pm   | Banquet at [**Rustler's Rooste**](https://www.rustlersrooste.com/) |            |            |            |

::: {.content-visible when-profile="local"}

::: {.callout-note}

* Based on this original plan, there will be 12 plenary talks, 72 presentations in parallel sessions, and a number of poster presentations in 2 poster sessions.

* We may want to reduce the number of plenary talks to make room for more parallel sessions. 

* We can have at least three tracks:
  * Bio-mediated Geotechnics
  * Bio-inspired Geotechnics
  * Education, training, industrial collaboration, sustainability in Biogeotechnics

* For each track, we can have a few sessions targeting on different applications such as:
  * Bio-mediated
    * Hazard mitigation
    * Construction
    * Environmental remediation or restoration
  * Bio-inspired
    * Site investigation
    * Foundation
    * Cross-cutting
  * ETCS (successes and pitfalls)
    * Education
    * Training
    * Industrial collaborations
    * Sustainability

:::
:::

